This PDF is a Git Repository\\Containing its Own \LaTeX\ Source\\and a Copy of Itself

### 2017-05-10 article.tex
Added a note about it being a polyglot
Added a section on the %%EOF problem

>>>>

Okay, I have to admit something: There is one more challenge. You see,
the latest PDF standard, ISO~32000-1:2008, says
\begin{center}
\begin{tikzpicture}
\node at (0,0) (text) {\begin{minipage}{0.8\hsize}\small
The \emph{trailer} of a PDF file enables a conforming reader to
quickly find the cross-reference table and certain special
objects. Conforming readers should read a PDF file from its end. The
last line of the file shall contain only the end-of-file
marker, \texttt{\%\%EOF}.
\end{minipage}};
\node[anchor=north east] at (text.north west) {\LARGE``};
\node[anchor=south west] at (text.south east) {\LARGE''};
\end{tikzpicture}
\end{center}
Granted, we are producing a PDF that conforms to version~1.4 of the
specification, which doesn't appear to have that requirement.
However, at least as early as version 1.3, the specification did have
an implementation note that Acrobat requires the \texttt{\%\%EOF} to
be within the last 1024 bytes of the file.  Either way, that's not
guaranteed to be the case for us, especially since we are moving the
PDF to be at the beginning of the packfile.  There are almost
certainly going to be trailing bytes after the PDF's \texttt{\%\%EOF},
and if the git repository is large, those are likely to be more than
1024 bytes.

Fortunately, most common PDF readers don't seem to care how many
trailing bytes there are, at least when the PDF is version~1.4.
Unfortunately, some readers such as Adobe's try to be ``helpful,''
silently ``fixing'' the problem and offering to save the fixed version
upon exit.  We can at least partially fix the PDF, ensuring that
the \texttt{\%\%EOF} is exactly 20 bytes of the end of the file, by
creating a second uncompressed git object as the very end of the
packfile (right before the final 20~byte SHA-1 checksum).  We could
then move the trailer from the end of the original PDF at the start of
the pack to the new git object at the end of the pack.  Finally, we
could encapsulate the ``middle'' objects of the packfile inside a PDF
stream object, such that they are ignored by the PDF.  The tricky part
is that we would have to know how many bytes will be in that
stream \emph{before} we add the PDF to the git database.  That's
theoretically possible to do \textit{a priori}, but it'd be very labor
intensive to pull off.  Furthermore, using this approach will
completely break the inner PDF that is produced by cloning the
repository, since its trailer will then be in a separate file.
Therefore, I chose to live with Adobe's helpfulness and not pursue
this fix for the PoC.

This PDF is a git bundle containing its \LaTeX\ source, as well as all
of the code necessary to regenerate this polyglot.
